Visualising MSAs

### 2022-04-27 analysis/MSA.Rmd
Better phylogenies

tree3 <- rename_taxa(tree3, rename_df, old, new)
p3 <- ggtree(tree3) + geom_tiplab(fontface='italic')
p3 <- p3 + geom_nodelab(aes(subset=label>80))
p3
```

@@

p3 <-  ggtree(tree3) + geom_tiplab(fontface='italic')
p3 <- p3 + geom_nodelab(aes(subset=label>80))
p3 + xlim_tree(2.1)
```

>>>>

tree3 <- rename_taxa(tree3, rename_df, old, new)
p3 <- ggtree(tree3) + geom_tiplab(fontface='italic')
p3 <- p3 + geom_nodelab(aes(subset=label>80), label='*')
p3+ ggplot2::xlim(0,2.5)

```{r}
muhtree <- ggtree(tree3)
my_data <- muhtree$data
my_data <- my_data %>% mutate(support = replace_na(as.numeric(label), 0))
root <- rootnode(tree3)

good_p <- ggtree(tree3)  %<+% my_data  +
  geom_tiplab(fontface = 'italic') +
  geom_point2(aes(
    subset = !isTip & node != root,
    fill = cut(support, c(-1, 70, 90, 100))
  ),
  shape = 21,
  size = 4) +
  scale_fill_manual(
    values = c('#d95f02', '#7570b3', '#1b9e77'),
    labels = expression(BP < 70, 70 <= BP * " < 90", BP >= 90),
    name = 'Bootstrap Percentage',
    breaks = c('(-1,70]', '(70,90]', '(90,100]')
  ) +
  ggplot2::xlim(0, 2.5) +
  theme_tree(legend.position = 'bottom')
good_p
```

```{r}
cowplot::save_plot(good_p, filename = 'output/SOS3_better_phylogeny.png')
```

@@

p3 <-  ggtree(tree3) + geom_tiplab(fontface='italic')
p3 <- p3 + geom_nodelab()
p3 + xlim_tree(2.1)
```

```{r}
muhtree <- ggtree(tree3)
my_data <- muhtree$data
my_data <- my_data %>% mutate(support = replace_na(as.numeric(label), 0))
root <- rootnode(tree3)

good_p <- ggtree(tree3)  %<+% my_data  +
  geom_tiplab(fontface = 'italic') +
  geom_point2(aes(
    subset = !isTip & node != root,
    fill = cut(support, c(-1, 70, 90, 100))
  ),
  shape = 21,
  size = 4) +
  scale_fill_manual(
    values = c('#d95f02', '#7570b3', '#1b9e77'),
    labels = expression(BP < 70, 70 <= BP * " < 90", BP >= 90),
    name = 'Bootstrap Percentage',
    breaks = c('(-1,70]', '(70,90]', '(90,100]')
  ) +
  ggplot2::xlim(0, 2.5) +
  theme_tree(legend.position = 'bottom')
good_p
```
```{r}
cowplot::save_plot(good_p, filename = 'output/EIN3_better_phylogeny.png')
```
